\begin{flushleft}
\textbf{\Large{Value Numbering}}
\end{flushleft}
Prior research has shown that value numbering can increase opportunities for PRE.
LLVM presently has a GVN-PRE pass which exploits this. However, value numbering in 
GVN-PRE is tightly coupled with the code for removing redundancies, and hence
we deem it not useful for our purposes. We have written our own value numbering
pass which feeds expression value numbers to the PRE stage. It should be noted,
     however, that we do not implement value numbering from scratch and use an
     old (now defunct) LLVM pass as a starting point. Most importantly, we
     augment the basic value numbering in the following ways - 
     
\begin{itemize}     
  \item Add the notion of leader expression (described below), with associated
  data structures and functions. 
  \item Functionality to support value-number-based bitvectors rather than
  expression-name-based bitvectors. 
  \item (Optimization 1) If the expression operator is one of these - AND, OR, CMP::EQ
  or CMP::NE, and the operands have the same value number, we replace all uses
  accordingly and then delete the expression.
  \item (Optimization 2) If all operands of an expression are constants, then we 
  evaluate and propagate constants. 
  \item (Optimization 3) If one operand of an expression is a constant (0 or 1), then 
  we simplify the expression. e.g. {a+0 = a} , {b*1 = b}.
  \item (Optimization 4) If the incoming expressions to a \texttt{Phi} node have the same value 
  number, then the \texttt{Phi} node gets that same value number
\end{itemize}  
  As per our testing, optimizations 2 and 3 are also done by the reassociation
  pass in LLVM. In our final code we omit our implementation and rely on the
  more robust LLMV pass. Optimizations 1 and 4, however, are still our contribution.

\begin{flushleft}
\textbf{\large{Notion Of Leader Expression}}
\end{flushleft}
The value numbering algorithm computes the RPO solution as outlined in
\cite{Cooper95scc-basedvalue}. It goes over the basic blocks in reverse post
order and adds new expressions to a hash table based on the already computed
value numbers of the operands. We call an expression a `leader' if at the time
of computing its value number, the value number doesn't already exist in the
hash table. In other words, out of a potentially large set of expressions that
map to a particular value number, the leader expression was the first to be
encountered while traversing the function in reverse post order. Leader
expressions are vital to our algorithm as they are used to calculate the block
local properties of the dataflow equations.
